### 2007-01-15 Documentation/appendix.tex
*** empty log message ***

The \NOVA\ experiment can be simulated with the file {\tt NOvA.glb}. The description of the disapperance 
channels is taken from \cite{Yang_2004} and the description of the appearance channels follows 
the proposal \cite{Ambats:2004js}. These references
should be cited if the file {\tt NOvA.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt NOvA.glb}, the following additional files are required: 
\bi
\item {\tt NOvAplus.dat} (NuMI neutrino flux -- $\nu_\mu$)
\item {\tt NOvAminus.dat} (NuMI neutrino flux -- $\bar{\nu}_\mu$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The \NOVA\ experiment uses a neutrino beam from the Fermilab NuMI beamline. The target power is 
1.2~MV which results in $10^{21}$~pot~$\mathrm{yr^{-1}}$ and 3~years $\nu$-running and 3~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Totally Liquid Scintillator Detector (TASD) is taken to be 
$\mathrm{m_{det} = 25 \,kt}$ at a baseline of L~=~812~km approximately 12~km off-axis to the beamline. The
energy resolution is $\mathrm{\sigma_e=10 \% \cdot \sqrt{E}}$ for electrons and  $\mathrm{\sigma_e=5 \% \cdot \sqrt{E}}$
for muons. The following rules are defined within {\tt NOvA.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.8 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} & & \\ \hline
Signal & $0.24 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} &  &  \\ \hline
Signal & $0.8 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} & & \\ \hline
Signal & $0.37 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0037 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\end{tabular}
\end{center}

@@

\subsection*{DoubleCHOOZ -- {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb}}

The files {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic version of these files were used within \cite{Huber:2006vr} which should be cited if the files 
{\tt Dchooz-near.glb} and {\tt Dchooz-far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt Dchooz-near.glb} and/or {\tt Dchooz-far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt Dchooz-near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Dchooz-near.glb} and {\tt Dchooz-far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

\subsection*{Variable neutrino factory with Silver Channel -- {\tt NFvar\_GoldSilver.glb}}

A variable neutrino factory scenario that includes the golden and silver appearance channels can be 
simulated with the file {\tt NFvar\_GoldSilver.glb}. The basic version was
used within \cite{Huber:2006wb} and the golden channel follows the neutrino factory scenarios from \cite{Huber:2002mx}
and the description of the silver channel follows \cite{Autiero:2003fu}. These
references should be cited if the file {\tt
NFvar\_GoldSilver.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar\_GoldSilver.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt ECCthreshold.dat} (list for ECC threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The beam and golden channel attributes are similar to {\tt NFvar.glb}. The parent energy of the muons can be set
in the range $\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline is set by the {\sf
AEDL}-Variable {\tt BASELINE}. For the silver channel an additional ECC detector with a fiducial mass
$\mathrm{m_{ECC} = 5\,kt}$ is assumed to be located at the same baseline as the MID detector. The energy
resolution of the silver channel is set to $\mathrm{\sigma_e=20\%\cdot E}$. The following additional rule
compared to {\tt NFvar.glb} is introduced to {\tt NFvar\_GoldSilver.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{$\tau$-Appearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.096 \, \otimes \, (\nu_e \rightarrow \nu_\tau)_\mathrm{CC}$ & & 0.15 & $10^{-4}$ \\
 & & & & \\
Background & $3.1\cdot 10^{-8} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & $2.0\cdot 10^{-8} \,
\otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $3.7\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $1.0\cdot 10^{-3} \,
 \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\tau)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $7.0 \cdot 10^{-7} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $7.0\cdot 10^{-7} \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$& 0.2 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{High Resolution/Low Threshold neutrino factory -- \\{\tt NFvar\_hR\_lT.glb}}

A variable neutrino factory hybrid detector scenario can be simulated with the file {\tt NFvar\_hR\_lT.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt NFvar\_hR\_lT.glb} is used for a scientific publication or a talk.
For calculations that involve {\tt NFvar\_hR\_lT.glb}, the same additional files as for {\tt NFvar.glb} are
required and the {\sf AEDL}-Variables {\tt emax} and {\tt BASELINE} have to be set. {\tt NFvar\_hR\_lT.glb} 
implements a lower threshold ($\mathrm{\sim\,1\,GeV}$) at a higher energy resolution
$\mathrm{\sigma_e=15\%\cdot E + 0.085\, MeV}$ where the constant term represents 
the effects from Fermi Motion. The background rejection is introduced energy dependent as 
$10^{-3}/\mathrm{E^2}$ and matches {\tt NFvar.glb} at higher energies. The following rules are defined within {\tt NFvar\_hR\_lT.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.5 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.5 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 & $1.0 \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

IS THAT CORRECT? MR: WHAT HAPPENS TO OLD BETA BEAM FILES [WW]?

>>>>

The \NOVA\ experiment can be simulated with the file {\tt NOvA.glb}. The description of the disapperance 
channels is taken from \cite{Yang_2004} and the description of the appearance channels follows 
the proposal \cite{Ambats:2004js}. These references
should be cited if the file {\tt NOvA.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt NOvA.glb}, the following additional files are required: 
\bi
\item {\tt NOvAplus.dat} (NuMI neutrino flux -- $\nu_\mu$)
\item {\tt NOvAminus.dat} (NuMI neutrino flux -- $\bar{\nu}_\mu$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The \NOVA\ experiment uses a neutrino beam from the Fermilab NuMI beamline. The target power is 
1.12~MV which results in $10^{21}$~pot~$\mathrm{yr^{-1}}$ and 3~years $\nu$-running and 3~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Totally Liquid Scintillator Detector (TASD) is taken to be 
$\mathrm{m_{det} = 25 \,kt}$ at a baseline of L~=~812~km approximately 12~km off-axis to the beamline. The
energy resolution is $\mathrm{\sigma_e=10 \% \cdot \sqrt{E}}$ for electrons and  $\mathrm{\sigma_e=5 \% \cdot \sqrt{E}}$
for muons. The following rules are defined within {\tt NOvA.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.8 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} & & \\ \hline
Signal & $0.24 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} &  &  \\ \hline
Signal & $0.8 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} & & \\ \hline
Signal & $0.37 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0037 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\end{tabular}
\end{center}

@@

\subsection*{DoubleCHOOZ -- {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}}

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic version of these files were used within \cite{Huber:2006vr} which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

\subsection*{Variable neutrino factory with Silver Channel -- {\tt NF\_GoldSilver.glb}}

A variable neutrino factory scenario that includes the golden and silver appearance channels can be 
simulated with the file {\tt NF\_GoldSilver.glb}. The basic version was
used within \cite{Huber:2006wb} and the golden channel follows the neutrino factory scenarios from \cite{Huber:2002mx}
and the description of the silver channel follows \cite{Autiero:2003fu}. These
references should be cited if the file {\tt
NFvar\_GoldSilver.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar\_GoldSilver.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt ECCthreshold.dat} (list for ECC threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The beam and golden channel attributes are similar to {\tt NFvar.glb}. The parent energy of the muons can be set
in the range $\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline is set by the {\sf
AEDL}-Variable {\tt BASELINE}. For the silver channel an additional ECC detector with a fiducial mass
$\mathrm{m_{ECC} = 5\,kt}$ is assumed to be located at the same baseline as the MID detector. The energy
resolution of the silver channel is set to $\mathrm{\sigma_e=20\%\cdot E}$. The following additional rule
compared to {\tt NFvar.glb} is introduced to {\tt NF\_GoldSilver.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{$\tau$-Appearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.096 \, \otimes \, (\nu_e \rightarrow \nu_\tau)_\mathrm{CC}$ & & 0.15 & $10^{-4}$ \\
 & & & & \\
Background & $3.1\cdot 10^{-8} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & $2.0\cdot 10^{-8} \,
\otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $3.7\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $1.0\cdot 10^{-3} \,
 \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\tau)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $7.0 \cdot 10^{-7} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $7.0\cdot 10^{-7} \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$& 0.2 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{High Resolution/Low Threshold neutrino factory -- \\{\tt NF\_hR\_lT.glb}}

A variable neutrino factory hybrid detector scenario can be simulated with the file {\tt NF\_hR\_lT.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt NF\_hR\_lT.glb} is used for a scientific publication or a talk.
For calculations that involve {\tt NF\_hR\_lT.glb}, the same additional files as for {\tt NFvar.glb} are
required and the {\sf AEDL}-Variables {\tt emax} and {\tt BASELINE} have to be set. {\tt NF\_hR\_lT.glb} 
implements a lower threshold ($\mathrm{\sim\,1\,GeV}$) at a higher energy resolution
$\mathrm{\sigma_e=15\%\cdot E + 0.085\, MeV}$ where the constant term represents 
the effects from Fermi Motion. The background rejection is introduced energy dependent as 
$10^{-3}/\mathrm{E^2}$ and matches {\tt NFvar.glb} at higher energies. The following rules are defined within {\tt NF\_hR\_lT.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.5 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 &  $1.0 \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.5 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & (energy dep. rejection)
& 0.2 & $10^{-4}$\\
 & $1.0 \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & (energy dep. rejection)
&0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@
